Parsing Postfix log files

### 2007-10-09 doc/logparser.tex
Improved Lire review

    \item [Logparser/Lire] Lire is another general purpose log parser, but
        is developed under the GNU GPL\@.  Like other general purpose log
        parsers it doesn't extract enough data from Postfix logs to be
        worthwhile.  Development also seems to have stalled, with only a
        minor update since October 2004.  \newline
        \url{http://logreport.org/lire.html} \newline (Last checked
        2007/08/13.)

@@

    \item [Log Mail Analyser]~\cite{log-mail-analyser} has already been
        discussed in section~\ref{prior art}.

>>>>

    \item [Logparser/Lire] \textit{As any good system administrator knows,
        there's a lot more to keep track of in an active network than just
        webservers. Lire is hands down the most versatile log analysis
        software available today. Lire not only keeps you informed about
        your HTTP, FTP, and mail traffic, it also reports on your
        firewalls, your print servers, and your DNS activity. The ever
        growing list of Lire-supported services clearly outstrips any other
        software, in large part thanks to the numerous volunteers who have
        pioneered many new services and features. Lire is a total solution
        for your log analysis needs.\/}

        Lire is a general purpose log parser supporting many different
        types of log file.  Its Postfix parser extracts the following data
        from Postfix logs: \textit{The email servers' reports will show you
        the number of deliveries and the volume of email delivered by day,
        the domains from which you receive or send the most emails, the
        relays most used, etc.\/}; notably rejections are not mentioned.
        It supports multiple output formats (text, HTML, PDF and Excel 95).
        Logs can be imported and the extracted data saved, and reports
        generated later.  Accessing this data from another application is
        undocumented; given the source code it should be possible, with
        time, to access the data.

        Unlike other parsers reviewed, Lire does attempt to correlate log
        lines by queueid, but not by pid, so e.g.\ the complete list of
        recipients for a mail should be available.

        Lire does attempt to correlate log lines by queueid, not pid, but
        its hard coded parsing extracts only part of the available data and
        makes no attempt to deal with the other complications described in
        sections~\ref{complications} and~\ref{additional complications}.
        It stores data, but not in an easily accessible format.  It
        generates reports in multiple formats, but those reports do not
        appear to be customisable.

        \url{http://logreport.org/lire.html} \newline (Last checked
        2007/10/09.)

@@

    \item [Log Mail Analyser] has already been discussed in
        section~\ref{prior art}.
